Board games group recomendation using metadata

### 2024-12-09 paper v2/paper v2.tex
fix: translated figure labels

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{publishYear.png}
    \caption{Juegos por año de publicación}
    \label{fig:publishYear}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{distribucionRatings.png}
    \caption{Distribución de ratings de juegos}
    \label{fig:distribucionRatings}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{tematicasComunes.png}
    \caption{Temáticas más comunes en el dataset}
    \label{fig:tematicasComunes}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{mecanicasComunes.png}
    \caption{Mecánicas más comunes en el dataset}
    \label{fig:mecanicasComunes}
\end{figure}

@@

\subsection{Data preprocessing}
The first stage consists of reducing the dataset by not picking items without interactions and then dividing the...

@@

\section{Figures}

You may want to include figures in the paper to illustrate your approach and results. Such artwork should be centered, legible, and separated from the text. Lines should be dark and at least 0.5~points thick for purposes of reproduction, and text should not appear on a gray background.

Label all distinct components of each figure. If the figure takes the form of a graph, then give a name for each axis and include a legend that briefly describes each curve. Do not include a title inside the figure; instead, the caption should serve this function.

@@

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{icml2021.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses using yrcite.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent. If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{publishYear.png}
    \caption{Amount of games (y axis) by year of publication(x axis)}
    \label{fig:publishYear}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{distribucionRatings.png}
    \caption{Games rating distribution (1-10)}
    \label{fig:distribucionRatings}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{tematicasComunes.png}
    \caption{Most common game themes on the dataset}
    \label{fig:tematicasComunes}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\linewidth]{mecanicasComunes.png}
    \caption{Most common game mechanics on the dataset}
    \label{fig:mecanicasComunes}
\end{figure}

@@

\subsection{Data preprocessing}
The first stage consists of reducing the dataset. This is important because the amount of data makes it take too long to calculate any meaningful metrics.

Part of the reduction is already done on the dataset by default, since there are no games with less than 20 ratings. Since we are going to also reduce the amount of users, we will delete games further up to 40 ratings, and then pick from 4 different game classes.

@@

% \section{Figures}

% You may want to include figures in the paper to illustrate your approach and results. Such artwork should be centered, legible, and separated from the text. Lines should be dark and at least 0.5~points thick for purposes of reproduction, and text should not appear on a gray background.

% Label all distinct components of each figure. If the figure takes the form of a graph, then give a name for each axis and include a legend that briefly describes each curve. Do not include a title inside the figure; instead, the caption should serve this function.

@@

% \subsection{Citations and References}

% Please use APA reference format regardless of your formatter
% or word processor. If you rely on the \LaTeX\/ bibliographic
% facility, use \texttt{natbib.sty} and \texttt{icml2021.bst}
% included in the style-file package to obtain this format.

% Citations within the text should include the authors' last names and
% year. If the authors' names are included in the sentence, place only
% the year in parentheses using yrcite.

% Alphabetize references by the surnames of the first authors, with
% single author entries preceding multiple author entries. Order
% references for the same authors by year of publication, with the
% earliest first. Make sure that each reference includes all relevant
% information (e.g., page numbers).

% Please put some effort into making references complete, presentable, and
% consistent. If using bibtex, please protect capital letters of names and
% abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
% in your .bib file.
